The {TestIdeals} package for \emph{Macaulay2}

### 2019-04-16 Fsing/TestIdealsPaper/TestIdeals.tex
Update TestIdeals.tex

This paper describes methods for computing objects and numerical invariants in prime characteristic commutative algebra, implemented in the \texttt{TestIdeals.m2} package for the computer algebra system \emph{Macaulay2}.
A ring $R$ of prime characteristic $p$ comes equipped with the Frobenius endomorphism
\[ F: R \to R \ \text{ given by } F(x) =  x^p,\]
which is the basis for many constructions and methods.
Notably, the Frobenius endomorphism can be used to detect whether a ring is regular \cite{KunzCharacterizationsOfRegularLocalRings}, and further, to quantify how far a ring is from being regular, measuring the severity of a singularity.

>>>>

This paper describes methods for computing objects and numerical invariants in prime characteristic commutative algebra, implemented in the \texttt{TestIdeals.m2} package for the computer algebra system \emph{Macaulay2} \cite{M2}.
A ring $R$ of prime characteristic $p$ comes equipped with the Frobenius endomorphism
\[ F: R \to R \ \text{ given by } F(x) =  x^p,\]
which is the basis for many constructions and methods.
Notably, the Frobenius endomorphism can be used to detect whether a ring is regular \cite{KunzCharacterizationsOfRegularLocalRings}, and further, to quantify how far a ring is from being regular, measuring the severity of a singularity.
